A partisan affair: Mapping patronage in municipal bureaucracies of Brazil

### 2021-03-29 paper/draft.tex
final paper

Who benefits from patronage? What motivates allocation of public sector jobs in the first place? A

>>>>

Who benefits from patronage in local bureaucracies? Are there systematic differences between patronage beneficiaries and their non-partisan counterparts? And what are its implications on local public sector employment? Patronage in developing countries is a wide-spread and well-documented phenomenon \citep{robinson2013political, grindle2012jobs}. Previous research on the topic has shown that the prevalence of patronage appointments in the bureaucracy can lead to lower economic development \citep{evans1999bureaucracy,kohli2004state}, as well as instability in the execution of policy and the primacy of short-term political gains over long-term provision of public goodss \citep{remmer2007political}.
